Grow with the flow: a latitudinal cline in physiology is associated with more variable precipitation in \textit{Erythranthe cardinalis}

### 2017-09-02 ms/ms.Rnw
mortality effect size analysis

  system.time(
  ciMerModMort <- confint(fitMort, method = "boot", FUN = fn, nsim = 1e3, seed = 925200709,
                          parallel = "multicore", ncpus = 4L)
)

  # tmp  <- ciMerModMort
  # ciMerModMort <- tmp
  ciMerModMort <- as.data.frame(ciMerModMort)
  ciMerModMort$estimate <- c(
    fit[c("PopID", "PopID:TempTrt", "PopID:WaterTrt", "PopID:TempTrt:WaterTrt"),
        "Chisq"],
    fit["PopID", "Chisq"] - fit["PopID:TempTrt", "Chisq"],
    fit["PopID", "Chisq"] - fit["PopID:WaterTrt", "Chisq"],
    fit["PopID", "Chisq"] - fit["PopID:TempTrt:WaterTrt", "Chisq"])

      rownames(ciMerModPhoto) <- c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
                               "PopID - PopID:TempTrt", "PopID - PopID:WaterTrt")
  rm(fit)

  saveRDS(ciMerModMort, paste0(pathDat, "/ciMerModMort.rds"))
  ciMerModMort <- readRDS(paste0(pathDat, "/ciMerModMort.rds"))
  # Figure of reaction norms
  d <- subset(master, !is.na(master$DiedFromStress))
  tab <- tapply(d$DiedFromStress, list(d$PopID, d$WaterTrt, d$TempTrt), 
                function(X) 1 - length(which(X)) / length(X))
  pdf(paste(pathFig, "/FigureS_MortRxnNorm.pdf", sep = ""), 4, 4, useDingbats = F)
  par(mai = c(0.5, 1, 0.5, 0.25))
  plot(0, 0, type = "n", xlab = "", ylab = "", axes = F, frame.plot = T, 
       xlim = c(1, 4), ylim = c(0, 1))
  abline(v = 2.5)
  mtext(side = 3, c("Cool", "Hot"), at = c(1.625, 3.375))
  mtext(side = 1, c("Wet", "Dry", "Wet", "Dry"), at = c(1, 2.25, 2.75, 4))
  mtext(side = 1, "Water Treatment", font = 2, cex = 1.25, line = 1.5)
  mtext(side = 3, "Temperature Treatment", font = 2, cex = 1.25, line = 1.5)
  axis(2, lwd = 0, lwd.ticks = 1, las = 1)
  title(ylab = "Survivorship", cex.lab = 1.5)

>>>>

  # Takes ~3 hours to run; use saved output
  # ciMerModMort <- confint(fitMort, method = "boot", FUN = fn, nsim = 1e3, 
  #                         seed = 925200709, parallel = "multicore", ncpus = 4L)
  # 
  # ciMerModMort <- as.data.frame(ciMerModMort)
  # ciMerModMort$estimate <- c(
  #   fit[c("PopID", "PopID:TempTrt", "PopID:WaterTrt", "PopID:TempTrt:WaterTrt"),
  #       "Chisq"],
  #   fit["PopID", "Chisq"] - fit["PopID:TempTrt", "Chisq"],
  #   fit["PopID", "Chisq"] - fit["PopID:WaterTrt", "Chisq"],
  #   fit["PopID", "Chisq"] - fit["PopID:TempTrt:WaterTrt", "Chisq"])
  # 
  # rownames(ciMerModMort) <- c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
  #                             "PopID:TempTrt:WaterTrt", "PopID - PopID:TempTrt",
  #                             "PopID - PopID:WaterTrt", 
  #                             "PopID - PopID:TempTrt:WaterTrt")
  # rm(fit)
  # 
  # saveRDS(ciMerModMort, paste0(pathDat, "/ciMerModMort.rds"))
  ciMerModMort <- readRDS(paste0(pathDat, "/ciMerModMort.rds"))

  # Figure of reaction norms
  d <- subset(master, !is.na(master$DiedFromStress))
  tab <- tapply(d$DiedFromStress, list(d$PopID, d$WaterTrt, d$TempTrt), 
                function(X) 1 - length(which(X)) / length(X))
  pdf(paste(pathFig, "/FigureS_MortRxnNorm.pdf", sep = ""), 4, 4, useDingbats = F)
  par(mai = c(0.5, 1, 0.5, 0.25))
  plot(0, 0, type = "n", xlab = "", ylab = "", axes = F, frame.plot = T, 
       xlim = c(1, 4), ylim = c(0, 1))
  abline(v = 2.5)
  mtext(side = 3, c("Cool", "Hot"), at = c(1.625, 3.375))
  mtext(side = 1, c("Wet", "Dry", "Wet", "Dry"), at = c(1, 2.25, 2.75, 4))
  mtext(side = 1, "Water Treatment", font = 2, cex = 1.25, line = 1.5)
  mtext(side = 3, "Temperature Treatment", font = 2, cex = 1.25, line = 1.5)
  axis(2, lwd = 0, lwd.ticks = 1, las = 1)
  title(ylab = "Survivorship", cex.lab = 1.5)
